Size, Shape and Functionality Dependence of Solute Transport Mechanisms in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-03-06 Ben_Manuscripts/transport/Outline.tex
Outline updates

  Using four different methods, Rowley and Roux observed peaks in the radial
  distribution function for sodium coordinated with water at an O-Na distance 
  of between 2.3 and 2.5 \AA~\cite{rowley_solvation_2012}. We used 2.5 \AA as
  the distance cutoff.

@@

  The MSD of sodium and water is significantly larger in the 10 wt \% water system
  versus the 5 wt \% water system.
  \begin{itemize}
    %BJC: these numbers will change. This is for incomplete methanol systems. I will
    % redo calculations on pure water systems.
    \item Water moves about 65 times faster and sodium moves about 40 times faster
    in the 10 wt\% system.
    \item Water moves about 65 times faster than sodium in the 10 wt \% system and
    40 times faster than sodium in the 5 wt \% system. %BJC: weird coincidence
    \item The diffusivity of water in the 10 wt \% system is still only 1 \% that of 
    bulk water %BJC: 5.53e-07 versus 5.5e-05 cm^2/s
  \end{itemize}

@@

  \noindent Sodium coordinates with water far less than in bulk solution.
  \begin{itemize}
    \item On average, each sodium ion is coordinated to about 1.7 water molecules in 
    the 10 wt \% system and 1.15 water molecules in the 5 wt\% system.
    \item In bulk water, it is estimated that sodium coordinates with 5.6 - 5.8 water
    molecules~\cite{rowley_solvation_2012}
    \item The low levels of water coordination under confinement are likely driven
    in part by favorable interactions between sodium ions and carboxylate head groups.
    \item A dehydrated sodium ion is not shielded from the negatively charged carboxylate
    group.~\cite{ma_drastically_2019}
  \end{itemize}

  % BJC: This figure is from methanol simulations. Will be replaced by pure water
  % simulations
  % BJC: I can probably just report the averages rather than plot this
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{Na_water_coordination.pdf}
  \caption{}\label{fig:na_water_coordination}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{Na_hg_coordination.pdf}
  \caption{}\label{fig:na_hg_coordination}
  \end{subfigure}
  \end{figure}

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{all_5wt_tamsds.pdf}
  \caption{5 wt \% water}\label{fig:all_msds_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{all_10wt_tamsds.pdf}
  \caption{10 wt \% water}\label{fig:all_msds_10wt}
  \end{subfigure}
  %BJC: missing a few since those simulations just got started
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msd_radius_5wt.pdf} 
  \caption{5 wt \% water}\label{fig:msd_radius_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msd_radius_10wt.pdf} 
  \caption{10 wt \% water}\label{fig:msd_radius_10wt}
  \end{subfigure}
  \caption{}\label{fig:msds}
  \end{figure}

  \noindent On the timescales simulated in our study, we observe subdiffusive behavior.
  %, providing the beginnings of an answer to question~\ref{question:mechanisms}.
  \begin{itemize}  
    \item Figure~\ref{fig:example_ztraces} plots the $z$-coordinate versus time of
  	3 representative ethanol centers of mass in the 10 wt \% water system.
  	\item There are clear periods of entrapment separated by relatively large hops.
	\item The MSD calculated based on all ethanol molecules is plotted in 
	Figure~\ref{fig:example_msd} and is sublinear.
	\item The long periods of entrapment likely lead to this sublinear, and thus
	subdiffusive, behavior.
  \end{itemize}

  Solutes partition out of the pore into the head group region and beyond which
  may lead to radially dependent transport mechanisms.
  \begin{itemize}
    \item It is clear from Figure~\ref{fig:example_ztraces} that the longest 
    periods of entrapment usually occur when solutes are far from the pore
    center.
    \item There is a high resistance to movement in the dense head group and
    tail regions.
    \item When hops occur, and where there is the most $z$-positional noise, 
    solutes are generally close to the pore center.
    \item Solutes can move relatively freely when they enter the pore region
    which is primarily composed of water molecules and sodium ions.
  \end{itemize}

@@

  %BJC: need to check whether sodium ion association is exhibited by all solutes
  In addition to solute trapping in dense monomer regions, we observe a second
  trapping mechanism caused by preferential hydrogen bonding between 
  hydrogen bond donor solutes and monomer carboxylate groups. 
  \begin{itemize}
    \item Of the time spent donating hydrogen atom(s), x \% of the hydrogen
    bonds occur between solutes and carboxylate groups as opposed to solutes
    with water. 
    \item This shows a high preference for the carboxylate anions since there
    are 5 times more water molecules in the system.
    \item The carboxylate oxygen atoms have a slightly higher partial negative
    charge than water molecules.
    \item Additionally, on average, each sodium ion is coordinated to 3 water
    molecules. Roughly all of the water in the pore region is usually coordinated
    to a sodium ion which decreases their availability to solutes.
  \end{itemize}

@@

%  \noindent The direction of each hop is anti-correlated to the direction of the previous hop.
  \noindent Transport may be better described by a subordinated fractional brownian motion 
  (sFBM) model.
  \begin{itemize}
  	\item Figure~\ref{fig:example_autocovariance} shows the autocovariance function of 
  	ethanol step vectors. % BJC: vectors because includes magnitude + direction. Better word?
  	\item The negative autocovariance at low values of k indicates anti-correlation
  	between hops. 
  	\item If solutes followed a pure CTRW mechanism, the autocovariance function would
  	decay to zero immediately.
  	\item Although the autocovariance function is relatively noise, due to the somewhat small
  	number of hops observed over the course of each solute trajectory, there is the least 
  	uncertainty at k=1, the most insightful data point. This behavior is consistent across
  	all solutes molecules. % Can put error bars on points
  	\item Therefore, we believe transport can be described as subordinated fractional Brownian
  	motion where the leading process is a CTRW with hops whose direction is dictated by the parent
  	process, FBM.
  	\item Future publications will focus on modeling the solute's transport characteristics
  	with an sFBM model
  	\item We will draw on these observations only in a qualitative sense for the remainder of this work.
  \end{itemize}

@@

  We will revisit our observations in the the context of specific groups of 
  molecules in the discussion that follows.

@@

  The MSD of methanol, ethanol, propanol and butanol descends in order of 
  their molecular weight, however, methanol travels faster than expected.  %BJC: find approximate relationship between MW and mobility
  \begin{itemize}
    \item The MSD of ethanol, propanol and butanol descend approximately
    linearly as expected form the Stokes-Einstein relationship  % BJC: maybe better to use wilke-chang version with correction factor
    \item However, methanol travels considerably faster based on this relationship. (See Figure~\ref{fig:msd_radius_simple_alcohol_rdf}
  \end{itemize}

  Methanol moves fast because it has the highest radial density near the pore center where
  the largest hops occur.
  \begin{itemize} 
    \item The radial density as a function of distance from the pore center
    for each alcohol is plotted in Figure~\ref{fig:simple_alcohol_rdf}.
    \item On average, the density of methanol in the pore center is only slightly
    less than the density near the head groups.
    \item All other alcohol molecules are most concentrated in the head group region.
  \end{itemize}

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{msd_radius_simple_alcohols.pdf}
  \caption{}\label{fig:msd_radius_simple_alcohol_rdf}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{simple_alcohol_rdf.pdf}
  \caption{}\label{fig:simple_alcohol_rdf}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{simple_alcohol_hbonds.pdf}
  \caption{}\label{fig:simple_alcohol_hbonds}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{butanol_CO.pdf}  %BJC: can add inset to plot showing butanol with highlighted O and C
  \caption{}\label{fig:butanol_CO}
  \end{subfigure}
  \caption{(a) The radial distribution functions of each simple alcohol shows a maximum close
  to the highest density of monomer head groups (dashed line, normalized for easier visual
  comparison). Methanol spends the largest proportion of time, relative to the other alcohols,
  near the pore center, which may help explain its fast dynamics. (b) Despite relatively little
  difference in the total number of hydrogen bond occurences, a given alcohol's preference
  towards hydrogen bonds with the carboxylate groups increases with molecule size. (c) The average
  location of butanol's oxygen atom is significantly closer to the pore center than its most distal
  carbon atom, suggesting that the molecule is oriented with hydrophobic tails pointing away from
  the pore center.}\label{fig:simple_alcohols}
  \end{figure}

@@

  Of the two diols, ethylene glycol moves significantly faster than propylene glycol
  due to propylene glycol's affinity for the monomer head groups.  
  \begin{itemize}
    \item Combined with an increase in size, the addition of a single methyl group to ethylene glycol
    increases propylene glycol's hydrophobic character and causes it to favor positions
    near monomer head groups.
    \item Both diols have comparable densities close to the pore center, however propylene glycol's
    density has a large peak near the monomer head groups relative to ethylene glycol.
    \item Propylene glycol can form more highly stablized hydrogen bonds with carboxylate groups,
    explaining the higher incidence of hydrogen bonds shown in Figure~\ref{fig:multi_hbonds}.
    \item These observations are further reflected in its dwell and hop length distributions
    (See Figure~\ref{fig:dwell_hop_PG_GCL}).
    \item Propylene glycol exhibits longer dwell times and a narrower distribution of 
    hop lengths than ethylene glycol. 
    \item Somewhat counterintuitively, there is a relatively high density of ethylene
    glycol molecules beyond the head group region. This likely contributes to the relatively
    large error bars on its MSD in Figure~\ref{fig:all_msds}. 
    %BJC: can show figure of radial density colored with hop lengths
    \item This implies that hops performed by ethylene glycol must be considerably larger
    than those by propylene glycol in order to result in consistently larger MSD values.
  \end{itemize}

@@

  The MSD of the solutes descend in order of their density close to the pore center.
  \begin{itemize}
    \item As shown in the radial density functions (Figure~\ref{fig:ketones_rdf}), 
    Acetic has a fairly uniform and high density within the pore region.
    \item Acetone spends relatively little time near the pore center with its
    peak density nearest the peak head group density.
  \end{itemize}

  The amides, urea and acetamide hydrogen bond with head groups relatively infrequently.
  \begin{itemize}
    \item Acetic acid hydrogen bonds with head groups nearly 20 times as frequently.
    \item Urea and Acetamide both have hydrogen bond donating nitrogen atoms, however
  	nitrogen is a weaker hydrogen bond donor than oxygen due to its lower electronegativity.
    \item The peaks in their radial density are closer to the pore center than 
    other solutes that hydrogen bond with carboxylate groups (see 
    Figure~\ref{fig:simple_alcohol_rdf} for example).
  \end{itemize}

  Urea stays close to pore center because it's hydrophilic
  Acetamide stays a little closer to pore walls because it has hydrophobic character
  That's why acetamide is slower
  Acetic Acid is being slowed down by hydrogen bonding (compare to methanol)
  Urea is slowed down by ..?

  Once again, the trends in the MSD can in large part be explained by the solutes'
  preference for water.
  \begin{itemize}
  	\item Urea, Acetic Acid and Acetamide are all capable of donating hydrogen bonds,
  	while acetone is the first instance of a molecule in this study that can only
  	accept hydrogen bonds. It follows that acetone has the slowest MSD of this grouping.
  	\item Urea and Acetamide both have hydrogen bond donating nitrogen atoms, however
  	nitrogen is a weaker hydrogen bond donor than oxygen due to its lower electronegativity.
  	\item Hence, Acetic Acid donates the greatest number of hydrogen bonds and has
  	the highest density throughout the pore region.
  	\item All other solutes show a higher preference for the tail region where three 
  	dimensional confinement directly contributes to a lower MSD.
  	\item Urea likely compensates for its loss of mobility in the head group region by
  	making large hops upon escape into the pore region.
  	\item Urea frequently moves between the head group and pore region because its planar
  	shape makes it easier to transition between regions.% could quantify transition frequency probably. It seems like it might yield something. But also might make things more ambiguous.
  	\item As the solutes become less polar, their MSD decreases. 
  	\item Acetamide has one less amine group than Urea and a corresponding smaller MSD.
  	\item Despite a peak in its density near the pore center due to its water solubility,
  	Acetone is the least polar and spends the most time outside the tail group region 
  	leading to the lowest MSD.
%  	\item With two nitrogen groups that hydrogen bond relatively infrequently, one might 
%  	expect Urea to exhibit much faster transport, however its MSD is comparable to
%  	the much stickier acetic acid. 
%  	\item Urea is highly soluble in water but not miscible in all proportions like 
%  	acetic acid or even acetone.
%  	\item Relative to acetic acid, acetamide, urea and acetone spend more time in the head group region.
%  	\item There is a large peak near the head groups, but \% of the urea molecules 
%  	are behind in the head group region.
%  	\item The structure of acetamide differs from acetic acid only by an amine group in place
%  	of a hydroxyl group.
%  	\item The weaker hydrogen bonding capability of acetamide and an extra nonpolar methyl group compared to
%  	Urea makes acetamide even more likely to partition. 
%  	\item Urea has two hydrogen bond donor nitrogen atoms. It is not surprising that
%  	its density is high near the pore center, particularly near the monomer head groups.
%  	
%  	\item Acetic acid, a carboxylic acid shows a relatively high density in the pore region, with 
%  	a peak close to the carboxylate groups.  %BJC: hbonds a lot 
%  	\item Acetone is stabilized by accepting hydrogen bonds from water in the pore region, but
%    its low polarity and planar shape gives it comparable stability when trapped between head groups.
%  	\item Acetone's has two prominent peaks in its radial density. One is in the pore region and the o
%  	other is relatively deep in the head group region.
  \end{itemize}

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ketone_rdf.pdf}
  \caption{}\label{fig:ketones_rdf}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ketone_ratio.pdf}
  \caption{}\label{fig:ketones_ratio}
  \end{subfigure}
  \end{figure}

@@

  %BJC: Could be a supporting figure
  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{SOH_trace.pdf}
  \caption{}\label{fig:SOH_trace}
  \end{subfigure}
  \caption{}
  \end{figure}

@@

  \noindent 2,3-Dimercapto-1-propanol exhibits slower transport than glycerol because it spends more time
  near monomer head groups. % BJC: should I give all the solutes nicknames (i.e. their residue names)?
  \begin{itemize}
    \item Glycerol frequently hydrogen bonds with more than one head group at a time.
    % BJC: can probably quantify the following:
    \item It can also hydrogen bond with water molecules which increases its stability
    in the pore region.
    \item 2-3-Dimercapto-1-propanol preferentially hydrogen bonds with head groups 
    so it gravitates towards the head group region.
  \end{itemize}

  \noindent DMSO has an average MSD nearly twice as large as acetone even though it
  is a slightly larger molecule.
  \begin{itemize}
    \item The radial density of DMSO is higher than acetone close to the pore center.
  	\item The pyramidal structure of DMSO may force it to spend more time closer to
  	the pore center.
  \end{itemize}

>>>>

  Using four different methods, Rowley and Roux observed peaks in the radial
  distribution function for sodium coordinated with water at an O-Na distance 
  of between 2.3 and 2.5 \AA~\cite{rowley_solvation_2012}. We used 2.5 \AA as
  the distance cutoff.  % BJC: this might be too strict. I've seen literature where they define 3.2 angstroms as the cutoff

@@

%  The MSD of sodium and water is significantly larger in the 10 wt \% water system
%  versus the 5 wt \% water system.
  \noindent Water's mobility is increased when pores are larger and less crowded.
  \begin{itemize}
    %BJC: these numbers will change. This is for incomplete methanol systems. I will
    % redo calculations on pure water systems.
    \item The MSD of water is about 65 times higher and the MSD of sodium is about 40
    times higher in the 10 wt\% system.
    \item Water moves about 65 times faster than sodium in the 10 wt \% system and
    40 times faster than sodium in the 5 wt \% system. %BJC: weird coincidence
    \item The diffusivity of water in the 10 wt \% system is still only 1 \% that of 
    bulk water %BJC: 5.53e-07 versus 5.5e-05 cm^2/s
  \end{itemize}

@@

  \noindent Sodium coordinates with far less water molecules than it does in 
  bulk solution.
  \begin{itemize}
    \item In bulk water, it is estimated that sodium coordinates with 5.6 - 5.8 water
    molecules~\cite{rowley_solvation_2012}
    \item In our system, on average, each sodium ion is coordinated to about 1.7 
    water molecules in the 10 wt \% system and 1.15 water molecules in the 5 wt\% 
    system.
    \item The low levels of water coordination under confinement are likely driven
    in part by favorable interactions between sodium ions and carboxylate head groups.
    \item A dehydrated sodium ion is not shielded from the negatively charged 
    carboxylate group.~\cite{ma_drastically_2019}
    \item On average, sodium ions coordinate with 0.5 head group oxygen atoms in the
    10 wt \% water system and 0.4 head group oxygen atoms in the 5 wt \% water system. 
    % BJC: I thought 5 wt \% might be a little higher. These numbers might be skewed by
    % sodium ions that are within cutoff of both carboxylate oxygen atoms. Might be
    % better to report average number of sodiums coordinated to a head group
  \end{itemize}

  % BJC: This figure is from methanol simulations. Will be replaced by pure water
  % simulations
  % BJC: I can probably just report the averages rather than plot this
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{Na_water_coordination.pdf}
  \caption{}\label{fig:na_water_coordination}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{Na_hg_coordination.pdf}
  \caption{}\label{fig:na_hg_coordination}  % No caption since this probably won't be a figure
  \end{subfigure}
  \end{figure}

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{all_5wt_tamsds.pdf}
  \caption{5 wt \% water}\label{fig:all_msds_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{all_10wt_tamsds.pdf}
  \caption{10 wt \% water}\label{fig:all_msds_10wt}
  \end{subfigure}
  %BJC: missing a few since those simulations just got started
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msd_radius_5wt.pdf} 
  \caption{5 wt \% water}\label{fig:msd_radius_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msd_radius_10wt.pdf} 
  \caption{10 wt \% water}\label{fig:msd_radius_10wt}
  \end{subfigure}
  \caption{The MSDs of solutes in the 5 wt \% water system (a) are significantly
  smaller than those of the solutes in the 10 wt \% water system (b). The
  MSDs are not a monotonic function of molecular size (c and d).}\label{fig:msds}
  \end{figure}

  \noindent On the timescales simulated in our study, solutes exhibit subdiffusive behavior.
  %, providing the beginnings of an answer to question~\ref{question:mechanisms}.
  \begin{itemize}  
    \item Figure~\ref{fig:example_ztraces} plots the $z$-coordinate versus time of
  	3 representative ethanol centers of mass in the 10 wt \% water system.
  	\item There are clear periods of entrapment separated by relatively large hops.
	\item The MSD calculated based on all ethanol molecules is plotted in 
	Figure~\ref{fig:example_msd} and is sublinear.
	\item The long periods of entrapment likely lead to this sublinear, and thus
	subdiffusive, behavior.
  \end{itemize}

  \noindent Solutes partition out of the pore into the head group region and beyond which
  may lead to radially dependent transport mechanisms.
  \begin{itemize}
    \item It is clear from Figure~\ref{fig:example_ztraces} that the longest 
    periods of entrapment usually occur when solutes are far from the pore
    center.
    \item There is a high resistance to movement in the dense head group and
    tail regions.
    \item When hops occur, and where there is the most $z$-positional noise, 
    solutes are generally close to the pore center.
    \item Solutes can move relatively freely when they enter the pore region
    which is primarily composed of water molecules and sodium ions.
  \end{itemize}

@@

  %BJC: need to check whether sodium ion association is exhibited by all solutes
  In addition to solute trapping in dense monomer regions, we observe a second
  trapping mechanism caused by preferential hydrogen bonding between 
  hydrogen bond donor solutes and monomer carboxylate groups. 
  \begin{itemize}
    \item Of the time spent donating hydrogen atom(s), x \% of the hydrogen
    bonds occur between solutes and carboxylate groups as opposed to solutes
    with water. 
    \item This shows a high preference for the carboxylate anions since there
    are 5 times more water molecules in the system.
    \item The carboxylate oxygen atoms have a slightly higher partial negative
    charge than water molecules.
    \item Additionally, on average, each sodium ion is coordinated to 1.7 water
    molecules. Roughly all of the water in the pore region is usually coordinated
    to a sodium ion which decreases their availability to solutes.
  \end{itemize}

  Finally, we see instances of solutes which become immobilized or slowed by 
  association with sodium counterions. 
  \begin{itemize}
    \item Much like water, the polarity of the solutes leaves partial negative
    charges which are stabilized through electrostatic interactions with sodium ions.
    \item There are many cases in which polar groups bind to sodium ions for at
    least a few time steps. 
    \item There are some cases where solutes become immobilized for long periods
    of time while in close proximity to a sodium ion.
    \item In Figure~\ref{fig:na_met_trace}, the oxygen atom of methanol stays
    within 2.5 \AA of a sodium ion for the entire length of a trapping occurence.
  \end{itemize}

  \begin{figure}[!htb]
  \centering
  \includegraphics[width=0.45\textwidth]{na_met_trace.pdf}
  \caption{The oxygen atom of methanol stays bound to the same sodium ion for
  the majority of the trapping occurence between 400 and 600 ns. Regions
  highlighted red or blue indicate times when methanol's oxygen atom is within 
  2.5 \AA~of a sodium ion. The color of the shaded regions is switched every time
  the oxygen atom becomes associated to a different sodium ion.}\label{fig:na_met_trace}
  \end{figure}

@@

%  \noindent The direction of each hop is anti-correlated to the direction of the previous hop.
  \noindent Transport may be better described by a subordinated fractional brownian motion 
  (sFBM) model.
  \begin{itemize}
  	\item Figure~\ref{fig:example_autocovariance} shows the autocovariance function of 
  	ethanol step vectors. % BJC: vectors because includes magnitude + direction. Is there a better word?
  	\item The negative autocovariance at low values of k indicates anti-correlation
  	between hops. 
  	\item If solutes followed a pure CTRW mechanism, the autocovariance function would
  	decay to zero immediately.
  	\item Although the autocovariance function is relatively noise, due to the somewhat small
  	number of hops observed over the course of each solute trajectory, there is the least 
  	uncertainty at k=1, the most insightful data point. This behavior is consistent across
  	all solutes molecules. % Can put error bars on points
  	\item Therefore, we believe transport can be described as subordinated fractional Brownian
  	motion where the leading process is a CTRW with hops whose direction is dictated by the parent
  	process, FBM.
  	\item Future publications will focus on modeling the solute's transport characteristics
  	with an sFBM model
  	\item We will draw on these observations only in a qualitative sense for the remainder of this work.
  \end{itemize}

@@

%  We will revisit our observations in the the context of specific groups of 
%  molecules in the discussion that follows.

@@

  The MSD of methanol, ethanol, propanol and butanol descends in order of 
  their molecular weight, however, methanol travels faster than expected.  %BJC: find approximate relationship between MW and mobility
  \begin{itemize}
    \item The MSD of ethanol, propanol and butanol descend approximately
    linearly as expected from the Stokes-Einstein relationship  % BJC: maybe better to use wilke-chang version with correction factor
    \item However, methanol travels considerably faster than suggested by the
    relationship. (See Figure~\ref{fig:msd_radius_simple_alcohol_rdf}
  \end{itemize}

  Methanol moves fast, not only because it is the smallest solute studied in this work, but
  because it has the highest radial density near the pore center where the largest hops occur.
  \begin{itemize}
    \item The radial density as a function of distance from the pore center
    for each alcohol is plotted in Figure~\ref{fig:simple_alcohol_rdf}.
    \item On average, the density of methanol in the pore center is only slightly
    less than the density near the head groups.
    \item All other alcohol molecules are most concentrated in the head group region.
  \end{itemize}

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{msd_radius_simple_alcohols.pdf}
  \caption{}\label{fig:msd_radius_simple_alcohol_rdf}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{simple_alcohol_rdf.pdf}
  \caption{}\label{fig:simple_alcohol_rdf}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{simple_alcohol_hbonds.pdf}
  \caption{}\label{fig:simple_alcohol_hbonds}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{butanol_CO.pdf}  %BJC: can add inset to plot showing butanol with highlighted O and C
  \caption{}\label{fig:butanol_CO}
  \end{subfigure}
  \caption{(a) The MSD of the simple alcohols decrease as a function of the solute size, however
  methanol's MSD is considerably higher than expected based on the Stokes-Einstein equation. 
  (b) The radial distribution functions of each simple alcohol shows a maximum close
  to the highest density of monomer head groups (dashed line, normalized for easier visual
  comparison). Methanol spends the largest proportion of time, relative to the other alcohols,
  near the pore center, which may help explain its fast dynamics. (c) Despite relatively little
  difference in the total number of hydrogen bond occurences, a given alcohol's preference
  towards hydrogen bonds with the carboxylate groups increases with molecule size. (d) The average
  location of butanol's oxygen atom is significantly closer to the pore center than its most distal
  carbon atom, suggesting that the molecule is oriented with hydrophobic tails pointing away from
  the pore center.}\label{fig:simple_alcohols}
  \end{figure}

@@

  Of the two diols, ethylene glycol moves significantly faster than propylene glycol
  due to propylene glycol's affinity for the monomer head groups.  
  \begin{itemize}
    \item Combined with an increase in size, the addition of a single methyl group to ethylene glycol
    increases propylene glycol's hydrophobic character and causes it to favor positions
    near monomer head groups.
    \item Both diols have comparable densities close to the pore center, however propylene glycol's
    density has a large peak near the monomer head groups relative to ethylene glycol.
    \item Propylene glycol can form more highly stablized hydrogen bonds with carboxylate groups,
    explaining the higher incidence of hydrogen bonds shown in Figure~\ref{fig:multi_hbonds}.
    \item These observations are further reflected in its dwell and hop length distributions
    (See Figure~\ref{fig:dwell_hop_PG_GCL}).
    \item Propylene glycol exhibits longer dwell times and a narrower distribution of 
    hop lengths than ethylene glycol. 
    \item Somewhat counterintuitively, there is a relatively high density of ethylene
    glycol molecules beyond the head group region probably due to its relatively small size.
    This likely contributes to the somewhat large error bars on its MSD in Figure~\ref{fig:msds}. 
    %BJC: can show figure of radial density colored with hop lengths
    \item This implies that hops performed by ethylene glycol must be considerably larger
    than those by propylene glycol in order to result in consistently larger MSD values.
  \end{itemize}

@@

  \noindent The MSD of the solutes descend in order of their density close to the pore center.
  \begin{itemize}
    \item As shown in the radial density functions (Figure~\ref{fig:ketones_rdf}), 
    Acetic acid has a fairly uniform and high density within the pore region.
    \item Acetone spends relatively little time near the pore center with its
    peak density nearest the peak head group density.
  \end{itemize}

  \noindent The amides, urea and acetamide, hydrogen bond with head groups relatively 
  infrequently, but regularly coordinate with sodium ions (See Figure~\ref{fig:ketones}).
  \begin{itemize}
    \item In an average frame, acetic acid participates in more than 12 hydrogen 
    bonds with monomer head groups while urea and acetamide participate in less than 2.
    \item Urea and Acetamide both have hydrogen bond donating nitrogen atoms, however
  	nitrogen is a weaker hydrogen bond donor than oxygen due to its lower electronegativity.
  	\item Given their lower propensity to hydrogen bond one might expect amides to partition
  	out of the pore and/or to move through the pore quickly, perhaps faster than methanol.
    \item The peaks in their radial density are still situated between the pore center and the
    head groups, but closer to the pore center than other solutes that hydrogen bond with 
    carboxylate groups (see Figure~\ref{fig:simple_alcohol_rdf}, for example).
    \item Both solutes spend about half of their time with their carbonyl oxygen atom 
    coordinated to a sodium ion which restrains the solutes to within the pore region
    %BJC: it's possible the solutes hop from sodium to sodium quickly meaning solutes are not always immobilized.
    %BJC: could look into lifetime of association
    \item Interestingly, the nitrogen atoms do not coordinate with any sodium ions despite
    a similar negative partial charge. The hydrogen atoms may shield this interaction.
  \end{itemize}

  Acetone has the lowest MSD of this set because it is primarily trapped near and behind 
  the head groups.
  \begin{itemize}
    \item On average, acetone coordinates with sodium with the same frequency as acetic acid 
    \item However, acetic acid spends more time in the pore center and therefore encounters
    more sodium ions.
    \item When an acetone molecule coordinates with a sodium ion, its polarity is 
    largely neutralized and it retreats towards the head group region where it can easily
    get trapped.
    \item Acetic acid and the amides and acetic acid have alternate hydrophlic
    groups when bound to sodium ions which increases their stability in the pore.
  \end{itemize}

%  Once again, the trends in the MSD can in large part be explained by the solutes'
%  preference for water.
%  \begin{itemize}
%  	\item Urea, Acetic Acid and Acetamide are all capable of donating hydrogen bonds,
%  	while acetone is the first instance of a molecule in this study that can only
%  	accept hydrogen bonds. It follows that acetone has the slowest MSD of this grouping.
%  	\item Urea and Acetamide both have hydrogen bond donating nitrogen atoms, however
%  	nitrogen is a weaker hydrogen bond donor than oxygen due to its lower electronegativity.
%  	\item Hence, Acetic Acid donates the greatest number of hydrogen bonds and has
%  	the highest density throughout the pore region.
%  	\item All other solutes show a higher preference for the tail region where three 
%  	dimensional confinement directly contributes to a lower MSD.
%  	\item Urea likely compensates for its loss of mobility in the head group region by
%  	making large hops upon escape into the pore region.
%  	\item Urea frequently moves between the head group and pore region because its planar
%  	shape makes it easier to transition between regions.% could quantify transition frequency probably. It seems like it might yield something. But also might make things more ambiguous.
%  	\item As the solutes become less polar, their MSD decreases. 
%  	\item Acetamide has one less amine group than Urea and a corresponding smaller MSD.
%  	\item Despite a peak in its density near the pore center due to its water solubility,
%  	Acetone is the least polar and spends the most time outside the tail group region 
%  	leading to the lowest MSD.
%  	\item With two nitrogen groups that hydrogen bond relatively infrequently, one might 
%  	expect Urea to exhibit much faster transport, however its MSD is comparable to
%  	the much stickier acetic acid. 
%  	\item Urea is highly soluble in water but not miscible in all proportions like 
%  	acetic acid or even acetone.
%  	\item Relative to acetic acid, acetamide, urea and acetone spend more time in the head group region.
%  	\item There is a large peak near the head groups, but \% of the urea molecules 
%  	are behind in the head group region.
%  	\item The structure of acetamide differs from acetic acid only by an amine group in place
%  	of a hydroxyl group.
%  	\item The weaker hydrogen bonding capability of acetamide and an extra nonpolar methyl group compared to
%  	Urea makes acetamide even more likely to partition. 
%  	\item Urea has two hydrogen bond donor nitrogen atoms. It is not surprising that
%  	its density is high near the pore center, particularly near the monomer head groups.
%  	
%  	\item Acetic acid, a carboxylic acid shows a relatively high density in the pore region, with 
%  	a peak close to the carboxylate groups.  %BJC: hbonds a lot 
%  	\item Acetone is stabilized by accepting hydrogen bonds from water in the pore region, but
%    its low polarity and planar shape gives it comparable stability when trapped between head groups.
%  	\item Acetone's has two prominent peaks in its radial density. One is in the pore region and the o
%  	other is relatively deep in the head group region.
%  \end{itemize}

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ketone_rdf.pdf}
  \caption{}\label{fig:ketones_rdf}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ketone_hbonds.pdf}
  \caption{}\label{fig:ketone_hbonds}
  \end{subfigure}
%  \begin{subfigure}{0.45\textwidth}
%  \includegraphics[width=\textwidth]{ketone_ratio.pdf}
%  \caption{}\label{fig:ketones_ratio}
%  \end{subfigure}
  \caption{(a) The radial density near the pore center (r = 0) decreases
  with decreasing solute MSD. (b) The amides hydrogen bond with water far
  less than acetic acid, however they tend to coordinate with sodium ions
  more frequently.}\label{fig:ketones}
  \end{figure}

@@

  %BJC: Could be a supporting figure
  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{SOH_trace.pdf}
  \caption{}\label{fig:SOH_trace}
  \end{subfigure}
  \caption{Mercaptoethanol exhibits transport behavior ranging from frequent hopping
  to lengthy trapping. Large hops generally occur near the pore center while 
  long entrapments occur while tangled among the monomer tails.}
  \end{figure}

@@

  \noindent 2,3-Dimercapto-1-propanol exhibits slower transport than glycerol because it spends more time
  near monomer head groups. % BJC: should I give all the solutes nicknames (i.e. their residue names)?
  \begin{itemize}
    \item Glycerol frequently hydrogen bonds with more than one head group at a time (See Figure~\ref{fig:multi_hbonds}).
    % BJC: can probably quantify the following:
    \item It can also hydrogen bond with water molecules which increases its stability
    in the pore region.
    \item 2-3-Dimercapto-1-propanol preferentially hydrogen bonds with head groups 
    so it gravitates towards the head group region.
  \end{itemize}

  \noindent DMSO has a comparable if not large MSD than acetone even though it
  is a slightly larger molecule.
  \begin{itemize}
    \item The radial density of DMSO is higher than acetone close to the pore center.
  	\item The pyramidal structure of DMSO may force it to spend more time closer to
  	the pore center.
  	%BJC: quantify sodium coordination O group of DMSO
  \end{itemize}
